Constructing a universe for the setoid model

### 2020-06-30 paper.tex
More paper writing

Previous work \cite{abel2019failure} seems to suggest that the strong transport
rule for proof-irrelevant identity types is a non-trivial addition to the
metatheory.
%
We would like to investigate a construction of the setoid universe that does not
require such rule, not only to avoid unnecessary extensions to the metatheory,
but also because we don't yet know whether $MLTT^{Prop}$ extended with this rule
is normalizing.

We want to figure out whether our inductive encoding of the setoid universe can
support universe induction. A related question is whether the alternative
definitions using induction-recursion and induction-induction can support it.

SeTT \cite{mpc19} and XTT \cite{xtt} are both syntactic representations of the
setoid model with similar design choices, like definitional
proof-irrelevance. We would like to know whether their respective notions of
models are equivalent, that is, whether we can obtain an XTT model from a SeTT
model, and vice versa. Since XTT universes support universe induction, it is
possible that we would need to extend our own universe with the same principle
(see discussion in Section~\ref{setoid-model} and the previous paragraph). A
further question is whether this mapping of models is functorial.

>>>>

As further work, we would like to investigate a construction of the setoid
universe that does not require a strong transport rule for the proof-irrelevant
identity type. Not only to avoid unnecessary extensions to the metatheory, but
also because we don't yet know whether $\mlttp$ extended with this rule is
normalizing.
%
Indeed, previous work in this respect \cite{abel2019failure} seems to suggest
that this rule is a non-trivial addition to the metatheory.

Additionally, we want to figure out whether our inductive encoding of the setoid
universe can support universe induction. A related question is whether the
alternative definitions using induction-recursion and induction-induction can
support it.

Another question regards the relationship between SeTT \cite{mpc19} and XTT
\cite{xtt}. Both systems are syntactic representations of the setoid model with
similar design choices, like definitional proof-irrelevance. We would like to
know whether their respective notions of models are equivalent, that is, whether
we can obtain an XTT model from a SeTT model, and vice versa. Since XTT
universes support universe induction, it is possible that we would need to
extend our own universe with the same principle (see discussion in
Section~\ref{setoid-model} and the previous paragraph). A further question is
whether this mapping of models is functorial.
